Outputs - civil servants' survey

### 2024-12-23 reports/paper_outputs_Dec_2024.qmd
Update paper_outputs_Dec_2024.qmd

@@

## Table 1 - Characteristics of survey sample and research population
```{r}
data_for_analysis_senior %>% data_frame()%>%
  dplyr::select(tenure,
         position_type,
         ranking,
         gender,
         age,
         education,
         religiosity,
         jurist)  %>%
  gtsummary::tbl_summary()
```

@@

## Causal mediation analysis

Exit

```{r}
# Load necessary package
library(mediation)
set.seed(2023)

t1 <- data_for_analysis_senior %>% 
  drop_na(BACKSLIDING_2,INTENT_EXIT_2,PROJECT_VOICE,PROJECT_EFFORT,PROJECT_POLITICIZATION,PROJECT_INFLUENCE)

# Mediator 1 model
med1_model <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=t1)

# Mediator 2 model
med2_model <- lm(PROJECT_INFLUENCE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=t1)

# Outcome model med 1
outcome_model_1 <-
  lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_POLITICIZATION,
            data=t1)

# Outcome model med 2
outcome_model_2 <-
  lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_INFLUENCE,
            data=t1)

# Mediation analysis for the first mediator with bootstrapping
mediation_result_exit_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_exit_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_exit_politicization) 
```

```{r}
summary(mediation_result_exit_influence)
```

Voice

# Outcome model med 1
outcome_model_1 <-
  lm(PROJECT_VOICE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_POLITICIZATION,
            data=t1)

# Outcome model med 2
outcome_model_2 <-
  lm(PROJECT_VOICE ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE +
            PROJECT_INFLUENCE,
            data=t1)

# Mediation analysis for the first mediator with bootstrapping
mediation_result_voice_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_voice_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_voice_politicization)
```

```{r}
summary(mediation_result_voice_influence)
```

Effort

# Outcome model med 1
outcome_model_1 <-
  lm(PROJECT_EFFORT ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
            PROJECT_POLITICIZATION,
            data=t1)

# Outcome model med 2
outcome_model_2 <-
  lm(PROJECT_EFFORT ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE + PAST_EFFORT + 
            PROJECT_INFLUENCE,
            data=t1)

# Mediation analysis for the first mediator with bootstrapping
mediation_result_work_politicization <-
  mediate(
    med1_model,
    outcome_model_1,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_POLITICIZATION",
    boot = TRUE,
    sims = 1000
  )

# Mediation analysis for the second mediator with bootstrapping
mediation_result_work_influence <-
  mediate(
    med2_model,
    outcome_model_2,
    treat = "BACKSLIDING_2",
    mediator = "PROJECT_INFLUENCE",
    boot = TRUE,
    sims = 1000
  )

# Summary of the results
```

```{r}
summary(mediation_result_work_politicization)
```

```{r}
summary(mediation_result_work_influence)
```

@@

## Exit 1

@@

```{r}
exit_mod1 <- lm(INTENT_EXIT_1 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

@@

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

@@

```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2,
            data=data_for_analysis_senior)

exit_mod3 <- exit_mod1 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

exit_mod4 <- exit_mod2 %>% update(.~.+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party)

#Table A8
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.ci = F,
                  show.se = T,
                  collapse.se = T,
                  terms = c("(Intercept)",
                            "BACKSLIDING_2",
                            "PROJECT_POLITICIZATION",
                            "PROJECT_INFLUENCE"))

@@

## Controls

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
            data=data_for_analysis_senior)
politicization_mod1_relig <- politicization_mod1 %>% update(.~.+religiosity)

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
influence_mod1_relig <- influence_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(politicization_mod1,politicization_mod1_relig,
                  influence_mod1,influence_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels)#,
                  dv.labels = c("Expected politicization","Expected influence")

@@

Model for exit, voice and work
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   
              PAST_POLITICIZATION + PAST_INFLUENCE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist+ ministry_by_party,
            data=data_for_analysis_senior)
exit_mod1_relig <- exit_mod1 %>% update(.~.+religiosity)

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
voice_mod1_relig <- voice_mod1 %>% update(.~.+religiosity)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT+ education+ gender +tenure+ position_type+ ranking+ age+ jurist + ministry_by_party)
work_mod1_relig <- work_mod1 %>% update(.~.+religiosity)

sjPlot::tab_model(exit_mod1,exit_mod1_relig,
                  voice_mod1,voice_mod1_relig,
                  work_mod1,work_mod1_relig,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2))

@@

```{r, fig.width=8,fig.height=6}
p1<- cars %>% ggplot(aes(x=speed))+ geom_histogram()

p1

#ggsave("p1.jpg",width = 8, height = 4,dpi=600)
```

>>>>

data_for_analysis_senior <- data_for_analysis_extended %>% 
  filter((ranking !="junior") %>% replace_na(TRUE)) %>% 
  filter(INTENT_EXIT_2>0|
          PROJECT_EFFORT>0|
           PROJECT_VOICE>0)
```

@@

## Table 1 - Characteristics of survey sample and research population
```{r}
data_for_analysis_senior %>% data_frame()%>%
  dplyr::select(tenure,
         position_type,
         ranking,
         gender,
         age,
         education,
         religiosity,
         jurist)  %>%
  gtsummary::tbl_summary()

@@

@@

## Exit 1 (online appendix A12)

@@

Alternative Measure for Exit 
```{r}

exit_mod1 <- lm(INTENT_EXIT_1 ~ 
                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

@@

exit_mod3 <- lm(INTENT_EXIT_1 ~ 
                  BACKSLIDING_2 + PAST_POLITICIZATION + PAST_INFLUENCE + education+ gender +tenure+ position_type+ ranking+ age+ jurist,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

exit_mod4 <- exit_mod3 %>% update(.~.+ PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

#Table A12.3
sjPlot::tab_model(exit_mod1,exit_mod2,
                  exit_mod3,exit_mod4,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("exit intention (first measure)"),each=4))

@@

## Models with controls (online appendix A8)

```{r}
predictor_labels <- c(
  "BACKSLIDING_2" = "Democratic backsliding",
  "PAST_POLITICIZATION" = "Past politicization",
  "PAST_INFLUENCE" = "Past influence",
  "PROJECT_POLITICIZATION" = "Expected politicization",
  "PROJECT_INFLUENCE" = "Expected influence",
  "PAST_VOICE" = "Past voice",
  "PAST_EFFORT" = "Past work effort"
)

data_for_analysis_senior <- data_for_analysis_senior %>%
  mutate(ministry_by_party = ministry_by_party %>% as.factor() %>% # Convert to factor
  relevel(ref = "Likud"), # Set "Other" as reference level
ranking = ranking %>% relevel(ref = "middle"), #set Very Senior as a based for ranking
education = education %>% relevel(ref = "bachelor")) #set bachelor as a based for education

@@

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
                            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                          data=data_for_analysis_senior)
politicization_mod1_controls <- politicization_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)

influence_mod1 <- politicization_mod1 %>%  update(PROJECT_INFLUENCE~.)
influence_mod1_controls <- influence_mod1 %>% update(.~.+religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)

sjPlot::tab_model(
                  politicization_mod1_controls,influence_mod1_controls,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = c("Expected politicization","Expected influence"),
                  order.terms = c(2:4,1))

@@

Model for exit, voice and work
```{r}
#Exit
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
exit_mod1_controls <- exit_mod1 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)

exit_mod2_controls <- exit_mod1_controls %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

#Voice
voice_mod1 <- lm(PROJECT_VOICE ~ 
                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
voice_mod1_controls <- voice_mod1 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)

voice_mod2_controls <- voice_mod1_controls %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

#Work
work_mod1 <- lm(PROJECT_EFFORT ~ 
                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))
work_mod1_controls <- work_mod1 %>%  update(.~. +religiosity + education+ gender +tenure+ position_type+ ranking+ age+ jurist)
work_mod2_controls <- work_mod1_controls %>%  update(.~. + PROJECT_POLITICIZATION + PROJECT_INFLUENCE)

sjPlot::tab_model(exit_mod1_controls,exit_mod2_controls,
                  voice_mod1_controls,voice_mod2_controls,
                  work_mod1_controls,work_mod2_controls,
                  show.est = F,
                  show.ci = F,
                  show.se = T,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                  dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=2))

@@

## Models with Junior Civil Servants (online appendix A8)

## include junior
data_for_analysis_all <- new_data %>% 
  filter(INTENT_EXIT_2>0|
           PROJECT_EFFORT>0|
           PROJECT_VOICE>0)

```{r}
politicization_mod1 <- lm(PROJECT_POLITICIZATION ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_all)

```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
                  BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
                data=data_for_analysis_all %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

## Heterogenious effects of backsliding, models with interactions (Online appendix A9)

Interaction with individual level variables
```{r}
exit_mod1 <- lm(INTENT_EXIT_2 ~ 
            BACKSLIDING_2 +   PAST_POLITICIZATION + PAST_INFLUENCE,
            data=data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE))

voice_mod1 <- exit_mod1 %>% update(PROJECT_VOICE~.+ PAST_VOICE)

work_mod1 <- exit_mod1 %>% update(PROJECT_EFFORT~.+ PAST_EFFORT)

Seniority

```{r}
exit_mod1_ranking_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*ranking)
voice_mod1_ranking_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*ranking)
work_mod1_ranking_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*ranking)

sjPlot::tab_model(exit_mod1_ranking_interaction,
                  voice_mod1_ranking_interaction,
                  work_mod1_ranking_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_ranking_interaction)
anova(voice_mod1_ranking_interaction)
anova(work_mod1_ranking_interaction)
```

```{r}
sjPlot::plot_model(work_mod1_ranking_interaction,type="int")
```

Tenure

```{r}
exit_mod1_tenure_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*tenure)
voice_mod1_tenure_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*tenure)
work_mod1_tenure_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*tenure)

sjPlot::tab_model(exit_mod1_tenure_interaction,
                  voice_mod1_tenure_interaction,
                  work_mod1_tenure_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_tenure_interaction)
anova(voice_mod1_tenure_interaction)
anova(work_mod1_tenure_interaction)
```

Education

```{r}
t1 <- data_for_analysis_senior %>% drop_na(PROJECT_POLITICIZATION,PROJECT_INFLUENCE) %>% 
  filter(education!="high-school")

exit_mod1_education_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*education,data=t1)
voice_mod1_education_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*education,data=t1)
work_mod1_education_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*education,data=t1)

sjPlot::tab_model(exit_mod1_education_interaction,
                  voice_mod1_education_interaction,
                  work_mod1_education_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_education_interaction)
anova(voice_mod1_education_interaction)
anova(work_mod1_education_interaction)
```

Legal education background (jurist)

```{r}
exit_mod1_jurist_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*jurist)
voice_mod1_jurist_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*jurist)
work_mod1_jurist_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*jurist)

sjPlot::tab_model(exit_mod1_jurist_interaction,
                  voice_mod1_jurist_interaction,
                  work_mod1_jurist_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_jurist_interaction)
anova(voice_mod1_jurist_interaction)
anova(work_mod1_jurist_interaction)
```

Age

```{r}
exit_mod1_age_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*age)
voice_mod1_age_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*age)
work_mod1_age_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*age)

sjPlot::tab_model(exit_mod1_age_interaction,
                  voice_mod1_age_interaction,
                  work_mod1_age_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_age_interaction)
anova(voice_mod1_age_interaction)
anova(work_mod1_age_interaction)
```

Gender

```{r}
exit_mod1_gender_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*gender)
voice_mod1_gender_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*gender)
work_mod1_gender_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*gender)

sjPlot::tab_model(exit_mod1_gender_interaction,
                  voice_mod1_gender_interaction,
                  work_mod1_gender_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_gender_interaction)
anova(voice_mod1_gender_interaction)
anova(work_mod1_gender_interaction)
```

Party by minister

```{r}
exit_mod1_ministry_by_party <- exit_mod1 %>% update(.~.+ ministry_by_party)
exit_mod1_ministry_by_party_interaction <- exit_mod1 %>% update(.~.+ BACKSLIDING_2*ministry_by_party)

voice_mod1_ministry_by_party <- voice_mod1 %>% update(.~.+ ministry_by_party)
voice_mod1_ministry_by_party_interaction <- voice_mod1 %>% update(.~.+ BACKSLIDING_2*ministry_by_party)

work_mod1_ministry_by_party <- work_mod1 %>% update(.~.+ ministry_by_party)
work_mod1_ministry_by_party_interaction <- work_mod1 %>% update(.~.+ BACKSLIDING_2*ministry_by_party)

sjPlot::tab_model(exit_mod1_ministry_by_party_interaction,
                  voice_mod1_ministry_by_party_interaction,
                  work_mod1_ministry_by_party_interaction,
                  show.est = F,
                  show.ci = F,
                  show.se = F,
                  show.std = T,
                  collapse.se = T,
                  emph.p=F,
                  string.est = "B",
                  string.std = "Beta",
                  string.pred = " ",
                  string.intercept = "Intercept",
                  pred.labels = predictor_labels,
                                    dv.labels = rep(c("Exit intention","Voice intention", "Work effort intention"),each=1))
```

```{r}
anova(exit_mod1_ministry_by_party_interaction)
anova(voice_mod1_ministry_by_party_interaction)
anova(work_mod1_ministry_by_party_interaction)
```
